Robust co-occurrence quantification for lexical distributional semantics experiments

### 2016-02-22 paper.tex
Abstract

\title{\ldots}

@@

\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, most notably shifting and context distribution smoothing. Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces with word vector  dimensionality of almost \textbf{200K}. As such, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC}.

>>>>

\title{Robust co-occurrence quantification for lexical distributional semantics experiments}

@@

\newcite{TACL570} suggested to optimize PMI with a  set of parameters adopted from predictive models of \newcite{mikolov2013efficient}, namely shifting and context distribution smoothing. Their experiments and thus the parameter selection recommendations use highly dimensional vector spaces with word vector  dimensionality of almost \textbf{200K}. As such, recent work on lexical distributional semantics with the results close to the state of the art involve vectors with a considerable dimensionality of hundreds of thousands \cite{baroni-dinu-kruszewski:2014:P14-1,kiela-clark:2014:CVSC,lapesa2014large}.
